Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-21 article.tex
pip install simbio

Modular code architecture makes code reusable, extensible, and easier to
maintain. Therefore, we split the code to define and simulate reaction
systems into three Python packages: symbolite, to create symbolic
expressions; poincaré, to define dynamical systems; and simbio, to
define reaction systems and interface with systems biology standards
such as \ac{SBML}. These are pure Python packages with standard dependencies
from the PyData scientific stack such as NumPy \cite{harrisArrayProgrammingNumPy2020}
and pandas \cite{mckinneyDataStructuresStatistical2010}. They are published in the \acf{PyPI}
, where links to the source code and documentation hosted
in GitHub can be found, and can be easily installed with
\texttt{pip\ install\ \textless{}package\_name\textgreater{}}.

>>>>

Modular code architecture makes code reusable, extensible, and easier to maintain.
Therefore, we split the code into three Python packages:
symbolite, to create symbolic expressions;
poincaré, to define dynamical systems;
and simbio, to define \acp{CRN} and interface with systems biology standards such as \ac{SBML}.
These are pure Python packages with standard dependencies from the PyData scientific stack
such as NumPy \cite{harrisArrayProgrammingNumPy2020} and pandas \cite{mckinneyDataStructuresStatistical2010}.
They are published in the \acf{PyPI},
where links to the source code and documentation hosted in GitHub can be found,
and can be easily installed with \texttt{pip\ install\ simbio},
which installs symbolite and poincare as dependencies.
